The NIR Corn Data Set

### 2019-08-22 MSc Project/paper_writing/MSc_dissertation_hongwei.tex
sample numbers

	\subsection{Loop times}
	\label{sec:Loop times}
	\begin{figure}[h]    % start of figure environment
		\centering           % put the graph(s) in the centre of the page (horizontally)
		\includegraphics[width=15.5cm, angle=0]{no_loop_time500.pdf}  % width changes size
		\vspace*{-0.25cm}    % manual adjustment of vertical spacing
		\caption{RMSECV and RMSEP under different loop times}          % a meaningful caption
		\label{fig:looptimes}               % label for the figure
	\end{figure}                        % end of figure environment

	\begin{figure}[h]    % start of figure environment
	\centering           % put the graph(s) in the centre of the page (horizontally)
	\includegraphics[width=8.5cm, angle=0]{Number_of_loop_times_mp5-1.pdf}  % width changes size
	\vspace*{-0.25cm}    % manual adjustment of vertical spacing
	\caption{SD under different loop times}          % a meaningful caption
	\label{fig:looptimes}               % label for the figure
\end{figure}                        % end of figure environment

>>>>

	\subsection{Loop times}
	\label{sec:Loop times}

	\begin{figure}[h]    % start of figure environment
		\centering           % put the graph(s) in the centre of the page (horizontally)
		\includegraphics[width=7.5cm, angle=0]{boxplot_RMSECV_loop_times_500.pdf}  % width changes size
		\includegraphics[width=7.5cm, angle=0]{boxplot_RMSEP_loop_times_500.pdf} % angle changes orientation
		\vspace*{-0.25cm}    % manual adjustment of vertical spacing
		\caption{The boxplot of RMSECV and RMSEP from PLSR of oil on m5 under different loop times}          % a meaningful caption
		\label{fig:sd_RMSECV_RMSEP}               % label for the figure
	\end{figure}                        % end of figure environment

\begin{figure}[h]    % start of figure environment
	\centering           % put the graph(s) in the centre of the page (horizontally)
	\includegraphics[width=7.5cm, angle=0]{sd_RMSECV_loop_times_500.pdf}  % width changes size
	\includegraphics[width=7.5cm, angle=0]{sd_RMSEP_loop_times_500.pdf} % angle changes orientation
	\vspace*{-0.25cm}    % manual adjustment of vertical spacing
	\caption{The standard deviation of RMSECV and RMSEP from PLSR of oil on m5 under different loop times}          % a meaningful caption
	\label{fig:sd_RMSECV_RMSEP}               % label for the figure
\end{figure}                        % end of figure environment
